---
title: "ST 558 Project 1"
author: "Kristi Ramey"
date: "9/23/2021"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
## Library needed:
```{r message=FALSE, warning=FALSE}

#Packages needed:
#install.packages("httr")
#install.packages("jsonlite")
#Libraries needed:
library(tidyverse)
library(httr)
library(jsonlite)
```
Connect to Pokemon API
```{r message=FALSE, warning=FALSE}
pokemondumpBLUE <- GET("https://pokeapi.co/api/v2/pokemon-color/blue/")
pokemondumpMALE <- GET("https://pokeapi.co/api/v2/gender/male/")
pokemondumpFEMALE <- GET("https://pokeapi.co/api/v2/gender/female/")

# Try to make sense of what info is given
pokemon_blue <- fromJSON(pokemondumpBLUE$url)
pokemon_male <- fromJSON(pokemondumpMALE$url)
pokemon_female <- fromJSON(pokemondumpFEMALE$url)

df_pokemon_blue <- pokemon_blue$pokemon_species[1]
# Number of Blue Pokemon
numb_blue <- nrow(df_pokemon_blue)
numb_blue

# Create a function to get a list of Pokemon of a certain color
color_FUN <- function(color){  
  base <- c("https://pokeapi.co/api/v2/pokemon-color/")
  color <- c(color)  
  slash <- c("/")
  api_color <- paste0(base, color, slash)
}
```
  pokemon_color <- fromJSON(api_color$url)
  df_pokemon_color <- pokemon_color$pokemon_species[1]
  return(df_pokemon_color)
  
  
  
}

test <- color_FUN(color = "blue")
test
```

pokemon_
## Pokemon data:

Pokemon data: https://pokeapi.co/
Render:
change input and output
rmarkdown::render(input = '_Rmd/2021-9-13-R-post.rmd', output_format = 'github_document', output_options = list(  keep_html = FALSE), output_dir = '_posts/')